---
title: "Assessment 1.1"
author: "Veronika Varaksina s4646146"
date: "`r format(Sys.Date(), '%d/%m/%y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# RMarkdown editing
The **rmarkdown package** helps you create dynamic analysis documents that combine code, rendered output (such as figures), and prose. You bring your *data, code, and ideas, and R Markdown renders* your content into a **polished document**.<br>
R Markdown documents can be rendered to many output formats including *HTML documents, PDFs, Word files, slideshows*, and more, allowing you to focus on the content while R Markdown takes care of your presentation.<br>
You can find information about basics of RMarkdown on the [official website](https://rmarkdown.rstudio.com/lesson-8.html).

```{r loading dataset}
fastfood <- read.csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv')
```

```{r first 10 rows of the dataset}
head(fastfood, 10)
```

```{r more than 1000 calories}
filter(fastfood, calories > 1000)
```

```{r save obs with over 40 fat and over 60 carb}
dont_eat_this <- filter(fastfood, total_fat > 40 & total_carb > 80)
```

```{r mcdonalds calories}
filter(fastfood, restaurant == 'Mcdonalds')
```

